### 2013-10-02 Rcode/intro.rmd
fixed bug in NegativeProb computation to exclude 0

@@

Now, we find the fitted values for $\pi$ are mostly near 0, or at 2 (the alternative value).
```{r}
print(beta.ash)
print(beta.ash.auto)
print(beta.ash.vb.uniform)
print(beta.ash.vb.null)
```

@@

plot(sort(ss$beta),(1:length(ss$beta))/length(ss$beta),main="cdf of ss$beta, with fitted f overlaid",xlab="beta",ylab="cdf")
lines(x,cdf.ash(beta.ash,x),col=2,lwd=2)
lines(x,cdf.ash(beta.ash.auto,x),col=3,lwd=2)
lines(x,cdf.ash(beta.ash.vb.uniform,x),col=4,lwd=2)
lines(x,cdf.ash(beta.ash.vb.null,x),col=5,lwd=2)
```

>>>>

beta.ash.pm = ash(ss$betahat,ss$betasd,usePointMass=TRUE)

@@

Now, we find the fitted values for $\pi$ are mostly near 0, or at 2 (the alternative value).
```{r}
print(beta.ash)
print(beta.ash.auto)
print(beta.ash.vb.uniform)
print(beta.ash.vb.null)
print(beta.ash.pm)
```

@@

plot(sort(ss$beta),(1:length(ss$beta))/length(ss$beta),main="cdf of ss$beta, with fitted f overlaid",xlab="beta",ylab="cdf")
lines(x,cdf.ash(beta.ash,x),col=2,lwd=2)
lines(x,cdf.ash(beta.ash.auto,x),col=3,lwd=2)
lines(x,cdf.ash(beta.ash.vb.uniform,x),col=4,lwd=2)
lines(x,cdf.ash(beta.ash.vb.null,x),col=5,lwd=2)
lines(x,cdf.ash(beta.ash.pm,x),col=6,lwd=2)
```

[for testing: compare results with point mass and without]
```{r}
  plot(beta.ash$PositiveProb)
  points(beta.ash.pm$PositiveProb,col=2)
```

```{r}
  plot(beta.ash$ZeroProb)
  points(beta.ash.pm$ZeroProb,col=2)
```
